### 2013-07-26 inst/doc/vingette.Rmd
readme recompiled (fix parsing error)

See the [EML generated](https://github.com/ropensci/eml/tree/master/inst/doc/my_eml_data.xml) by this example.

@@

```{r publish_figshare, eval=FALSE} <!-- We don't want to generate a DOI every time we run the vignette -->
id = eml_publish("my_eml_data.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML", destination="figshare")
```

`eml_publish` 
In return, figshare provides the object with a DOI, which is added to the EML.

>>>>

See the [EML generated](https://github.com/ropensci/reml/tree/master/inst/doc/my_eml_data.xml) by this example.

@@

<!-- We don't want to generate a DOI every time we run the vignette -->
```{r publish_figshare, eval=FALSE} 
id = eml_publish("my_eml_data.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML", destination="figshare")
```

In return, figshare provides the object with a DOI, which is added to the EML.
